Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars

### 2014-10-19 drafts/cfp/draft.tex
Recreated beforeAndAfter system; changed examples a little; moved vis.pl and main.pl to experiments/prolog/.

\documentclass{article}

\usepackage{amsmath}
\usepackage{listings}
\usepackage{anyfontsize}
\usepackage{subcaption}
\title{Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars}
\author{Eyal Dechter \& Josh Rule \& Josh Tenenbaum}

@@

\section{Experiments}
\section{Discussion}

>>>>

\documentclass[11pt, twocolumn]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{anyfontsize}
\usepackage{subcaption}
\title{Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars}
\author{Eyal Dechter \& Josh Rule \& Josh Tenenbaum}

@@

\section{Experiments}

\begin{tabular}{l l}
Question & $N_p=4$ \\ \hline
 after twenty comes \underline{\hspace{1cm}}? & twenty one \checkmark \\
 after forty five comes \underline{\hspace{1cm}}? & forty six \checkmark \\
 after forty seven comes \underline{\hspace{1cm}}? & forty eight  \checkmark \\
 after forty nine comes \underline{\hspace{1cm}}? & forty ten $\times$ \\
 after fifty nine comes \underline{\hspace{1cm}}? & fifty ten $\times$ \\
 after sixty one comes \underline{\hspace{1cm}}? & sixty two \checkmark \\
 after sixty three comes \underline{\hspace{1cm}}? & sixty four \checkmark \\
 after sixty four comes \underline{\hspace{1cm}}? & sixty five \checkmark \\
 after sixty five comes \underline{\hspace{1cm}}? & sixty six \checkmark \\
 after sixty nine comes \underline{\hspace{1cm}}? & sixty ten \checkmark \\
 after seventy three comes \underline{\hspace{1cm}}? & seventy four \checkmark \\
 after seventy nine comes \underline{\hspace{1cm}}? & seventy ten $\times$ \\
 after ninety five comes \underline{\hspace{1cm}}? & ninety six \checkmark \\
 before twenty three comes \underline{\hspace{1cm}}? & twenty two \checkmark \\
 before thirty comes \underline{\hspace{1cm}}? & thirty eighty $\times$ \\
 before thirty eight comes \underline{\hspace{1cm}}? & thirty seven \checkmark \\
 before forty one comes \underline{\hspace{1cm}}? & forty \checkmark \\
 before fifty three comes \underline{\hspace{1cm}}? & fifty two \checkmark \\
 before sixty eight comes \underline{\hspace{1cm}}? & sixty seven \checkmark \\
 before seventy two comes \underline{\hspace{1cm}}? & seventy one \checkmark \\
 before seventy three comes \underline{\hspace{1cm}}? & seventy two \checkmark \\
 before eighty five comes \underline{\hspace{1cm}}? & eighty four \checkmark \\
 before ninety two comes \underline{\hspace{1cm}}? & ninety one \checkmark \\
 before ninety three comes \underline{\hspace{1cm}}? & ninety two \checkmark \\
 before ninety five comes \underline{\hspace{1cm}}? &ninety four \checkmark \\

\end{tabular}

\begin{alignat*}{2}
&S(X Y) \leftarrow A_1(X, Y) : 1.0000 \\
&A_1(X Y, U V) \leftarrow A_2(X, U), A_3(V, Y) : 0.5002 \\
&A_2(before, comes) : 0.7316 \\
&A_4(after, comes) : 0.9990 \\
&A_1(X Y, U V) \leftarrow A_3(Y, V), A_4(X, U) : 0.3428 \\
&A_3(one, two) : 0.3993 \\
&A_3(two, three) : 0.2063 \\
&A_3(three, four) : 0.1093 \\
&A_1(X Y, U V) \leftarrow A_1(V, Y), A_4(X, U) : 0.0796 \\
&A_1(X Y, U V) \leftarrow A_1(Y, V), A_2(X, U) : 0.0712 \\
&A_3(four, five) : 0.0734 \\
&A_3(five, six) : 0.0502 \\
&A_3(six, seven) : 0.0355 \\
&A_3(eight, nine) : 0.0290 \\
&A_3(seven, eight) : 0.0271 \\
&A_2(fifty, fifty) : 0.0375 \\
&A_2(thirty, thirty) : 0.0361 \\
&A_2(eighty, eighty) : 0.0339 \\
&A_3(null, one) : 0.0231 \\
&A_2(forty, forty) : 0.0332 \\
&A_2(twenty, twenty) : 0.0310 \\
&A_2(seventy, seventy) : 0.0296 \\
&A_2(sixty, sixty) : 0.0274 \\
&A_2(ninety, ninety) : 0.0260 \\
&A_3(eighteen, nineteen) : 0.0064 \\
&A_3(sixteen, seventeen) : 0.0049 \\
&A_3(eleven, twelve) : 0.0044 \\
&A_3(nine, ten) : 0.0044 \\
&A_3(thirteen, fourteen) : 0.0044 \\
&A_3(fourteen, fifteen) : 0.0039 \\
&A_3(ten, eleven) : 0.0034 \\
&A_2(null, fifty) : 0.0043 \\
&A_3(eighty, null) : 0.0030 \\
&A_3(seventeen, eighteen) : 0.0030 \\
&A_1(X Y, U V) \leftarrow A_2(Y, X), A_3(V, U) : 0.0021 \\
&A_3(nine, sixty) : 0.0025 \\
&A_2(nine, seventy) : 0.0029 \\
&A_3(nine, forty) : 0.0020 \\
&A_1(X Y, U V) \leftarrow A_1(V, Y), A_2(X, U) : 0.0013 \\
&A_2(null, thirty) : 0.0022 \\
&A_2(nine, ninety) : 0.0022 \\
&A_3(twelve, thirteen) : 0.0015 \\
&A_3(fifteen, sixteen) : 0.0015 \\
&A_1(X Y, U V) \leftarrow A_2(V, X), A_3(Y, U) : 0.0008 \\
&A_3(null, comes) : 0.0010 \\
&A_1(X Y, U V) \leftarrow A_1(X, U), A_2(V, Y) : 0.0008 \\
&A_1(X Y, U V) \leftarrow A_1(X, U), A_2(Y, V) : 0.0008 \\
&A_2(twenty, after) : 0.0014 \\
&A_2(sixty, before) : 0.0007 \\
&A_3(nineteen, comes) : 0.0005 \\
&A_4(nine, thirty) : 0.0010 \\
&A_1(X Y, U V) \leftarrow A_1(X, U), A_4(Y, V) : 0.0004 \\
\end{alignat*} \\
\section{Discussion}
